---
title: "Web Mining"
author: "Jinfei Xue"
date: "Dec 2, 2018"
output:
  html_document:
    df_print: paged
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE, message=FALSE}
#install.packages("rvest")
#install.packages("dplyr")
#install.packages("knitr")
#install.packages("tidytext")
#install.packages("ggplot2")
library(rvest)
library(dplyr)
library(knitr)
library(tidytext)
library(ggplot2)
```

## War Timeline

```{r, warning=FALSE, message=FALSE}

url <- "https://www.iwm.org.uk/history/timeline-of-20th-and-21st-century-wars"
timeline <- url %>%
    read_html() %>%
    html_nodes(css = 'strong')%>%
  html_text() 

timeline <- timeline[!timeline %in% c("?C", "?C19", "?C199")]

war <- rep(NA, length(timeline))
time <- rep(NA, length(timeline))
for (i in 1:length(timeline)) {
  war[i] <- unlist(strsplit(timeline[i], ", "))[1]
  time[i] <- unlist(strsplit(timeline[i], ", "))[2]
}
war_tl <- unique(data.frame(war, time))
rownames(war_tl) <- 1:19
kable(war_tl)

```

## Common Factors Research

We first search for some researches about common factors of wars.

### The 8 Main Reasons for War
```{r}
url <- "https://owlcation.com/social-sciences/The-Main-Reasons-For-War"
# 8 Main Reasons
MRW <- url %>%
    read_html() %>%
    html_nodes(xpath = '//*[@id="txtd_45775170"]')%>%
  html_text() 
MRW <- unlist(strsplit(MRW, "\n"))
MRW <- MRW[-9]
# War examples for each main reason
war_ex <- url %>%
    read_html() %>%
    html_nodes(css = 'li strong')%>%
  html_text() 
war_ex <- war_ex[1:23]
# Combine
reasons <- rep(MRW, c(2,3,5,2,2,4,4,1))
mrw <- data.frame(reasons, war_ex)
kable(mrw)

```

We can see the eight main reasons for wars are "Economic Gain", "Territorial Gain", "Religion", "Nationalism", "Revenge", "Civil War", "Revolutionary War" and "Defensive War".

### The Causes of War
```{r}
url <- "https://www.theobjectivestandard.com/2014/10/causes-war-peace/"
# Wikipedia: Causes of Wars
causes <- url %>%
    read_html() %>%
    html_nodes(css = 'td:nth-child(1) strong')%>%
  html_text() 
kable(data_frame(causes))

```

## 3.1 the First World War 
```{r}
# The Origins of WWI
url_1 <- "https://www.historyonthenet.com/authentichistory/1914-1920/1-overview/1-origins/index.html"
ww1_1 <- url %>%
    read_html() %>%
    html_nodes(css = 'strong , .body_text .header')%>%
  html_text() 

url_2 <- "https://www.historyonthenet.com/authentichistory/1914-1920/1-overview/1-origins/index.html"
ww1_2 <- url %>%
    read_html() %>%
    html_nodes(css = 'strong , .body_text .header')%>%
  html_text() 

ww1 <- c(ww1_1, ww1_2)
kable(data_frame(WW1_Causes=ww1))
```

```{r}
url_ww1 <- c("https://www.historyonthenet.com/world-war-one-causes-2", 
             "https://www.thoughtco.com/causes-that-led-to-world-war-i-105515", 
             "https://www.historyhit.com/the-4-m-a-i-n-causes-of-world-war-one/", 
             "https://online.norwich.edu/academic-programs/resources/six-causes-of-world-war-i", 
             "https://medium.com/@dhireshnathwani/what-was-the-most-significant-cause-of-world-war-one-ww1-74bb9e815e37", 
             "https://www.firstworldwar.com/origins/causes.htm", 
             "https://www.ancienthistorylists.com/world-war-1/top-10-causes-of-world-war-1/")

ww11 <- url_ww1[1] %>%
  read_html() %>%
  html_nodes(css = 'h3+ p , p~ h2+ p , #mobile-in-article-1+ p , hr+ p')%>%
  html_text()

ww12 <- url_ww1[2] %>%
  read_html() %>%
  html_nodes(css = '#mntl-sc-block_3-0-1 p , #mntl-sc-block_2-0-16 p , #mntl-sc-block_2-0-13 p , #mntl-sc-block_2-0-10 p , #mntl-sc-block_2-0-7 p , #mntl-sc-block_2-0-4 p , .mntl-sc-block-heading__text , #mntl-sc-block_2-0-3 li , #mntl-sc-block_2-0-2 p')%>%
  html_text()

ww13 <- url_ww1[3] %>%
  read_html() %>%
  html_nodes(css = '.alignnone~ p , p p , .single li , p:nth-child(12) , h2~ h2 , p:nth-child(8)')%>%
  html_text()

ww14 <- url_ww1[4] %>%
  read_html() %>%
  html_nodes(css = 'p:nth-child(14) , h2+ p , .even h2 , #block-system-main p:nth-child(1)')%>%
  html_text()

ww15 <- url_ww1[5] %>%
  read_html() %>%
  html_nodes(css = '#7c29 , #4ec5+ .graf-after--p , #4ec5 , #0bd4 , #43d2 , #f0b7 , #3cde , #8c52 , #da23 , #42e2+ .graf-after--p , #42e2')%>%
  html_text()

ww16 <- url_ww1[6] %>%
  read_html() %>%
  html_nodes(css = 'ul~ h3+ p , #main li , p:nth-child(16) , p:nth-child(10) , #advertincontentlargeblock~ p+ p , #advertincontentlargeblock+ p')%>%
  html_text()

ww17 <- url_ww1[7] %>%
  read_html() %>%
  html_nodes(css = 'p:nth-child(33) , p:nth-child(31) , p:nth-child(29) , p:nth-child(23) , p:nth-child(19) , p:nth-child(17) , p:nth-child(14) , p:nth-child(10) , #post-4 p:nth-child(7) , p:nth-child(5) , p:nth-child(3)')%>%
  html_text()


ww1 <- c(ww11, ww12, ww13, ww14, ww15, ww16, ww17)
ww1_df <- data_frame(text = ww1)

ww1_n <- ww1_df %>% 
  unnest_tokens(word, text) %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE)
kable(ww1_n %>% filter(n > 20))

# create a visualization of the most common words 
ww1_n %>%
  filter(n > 20) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()
```





## 3.2 the Second World War 
```{r}
# The Origins of WWI
url <- "https://www.historyonthenet.com/authentichistory/1914-1920/1-overview/1-origins/index.html"
ww2 <- url %>%
    read_html() %>%
    html_nodes(css = 'strong , .body_text .header')%>%
  html_text() 
kable(data_frame(WW2_Causes = ww2))
```

```{r}
url_ww2 <- c("https://en.wikipedia.org/wiki/Causes_of_World_War_II", 
             "https://www.history.com/topics/world-war-ii/world-war-ii-history", 
             "https://www.thoughtco.com/world-war-ii-road-to-war-2361456", 
             "https://en.wikibooks.org/wiki/World_History/Causes_and_course_of_the_Second_World_War", 
             "https://www.theweek.co.uk/60237/how-and-why-did-world-war-2-start", 
             "https://www.historic-newspapers.co.uk/blog/what-started-world-war-two/")
             

ww21 <- url_ww2[1] %>%
  read_html() %>%
  html_nodes(css = 'p')%>%
  html_text()

ww22 <- url_ww2[2] %>%
  read_html() %>%
  html_nodes(css = '.m-detail--body p')%>%
  html_text()

ww23 <- url_ww2[3] %>%
  read_html() %>%
  html_nodes(css = 'p')%>%
  html_text()
ww23 <- ww23[-c(17, 18)]

ww24 <- url_ww2[4] %>%
  read_html() %>%
  html_nodes(css = 'p:nth-child(49) , p:nth-child(48) , p:nth-child(42) , p:nth-child(37) , p:nth-child(36) , p:nth-child(35) , p:nth-child(31) , p:nth-child(32) , h4+ p , p:nth-child(24) , p:nth-child(17) , h3+ p , h2+ p')%>%
  html_text()

ww25 <- url_ww2[5] %>%
  read_html() %>%
  html_nodes(css = 'h5+ p , p+ p')%>%
  html_text()

ww26 <- url_ww2[6] %>%
  read_html() %>%
  html_nodes(css = 'p:nth-child(40) , p:nth-child(37) , p:nth-child(34) , p:nth-child(29) , p:nth-child(28) , p:nth-child(23) , p:nth-child(22) , p:nth-child(21) , p:nth-child(20) , p:nth-child(19) , p:nth-child(14) , p:nth-child(11) , p:nth-child(3) , p:nth-child(2) , p:nth-child(8) , p:nth-child(1)')%>%
  html_text()

ww2 <- c(ww21, ww22, ww23, ww24, ww25, ww26)
ww2_df <- data_frame(text = ww2)

ww2_n <- ww2_df %>% 
  unnest_tokens(word, text) %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE)
kable(ww2_n %>% filter(n > 25))

# create a visualization of the most common words 
ww2_n %>%
  filter(n > 25) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()
```


## 3.3 the Korean War

```{r, message=FALSE}
url_kw <- c("https://www.historycrunch.com/causes-of-the-korean-war.html#/",
        "https://www.historycentral.com/korea/causes.html", 
        "http://time.com/3915803/korean-war-1950-history/", 
        "http://www.learnkoreanlanguage.com/causes-of-the-korean-war.html", 
        "http://www.bbc.co.uk/history/worldwars/coldwar/korea_hickey_01.shtml", 
        "https://www.enotes.com/homework-help/can-someone-answer-what-were-factors-leading-up-158481")
kw1 <- url_kw[1] %>%
  read_html() %>%
  html_nodes(css = '#wsite-content .paragraph font')%>%
  html_text()
kw2 <- url_kw[2] %>%
  read_html() %>%
  html_nodes(css = '.container .content p')%>%
  html_text()
kw3 <- url_kw[3] %>%
  read_html() %>%
  html_nodes(css = 'p')%>%
  html_text()
kw4 <- url_kw[4] %>%
  read_html() %>%
  html_nodes(css = 'p')%>%
  html_text()
kw5 <- url_kw[5] %>%
  read_html() %>%
  html_nodes(css = '.fr~ p , #four+ p , #three+ p , #two+ p , #one~ p')%>%
  html_text()
kw6 <- url_kw[6] %>%
  read_html() %>%
  html_nodes(css = '.anon-hide p')%>%
  html_text()
kw <- c(kw1, kw2, kw3, kw4, kw5, kw6)

kw_df <- data_frame(text = kw)

#my_stopwords <- data_frame(word = c("38th", "1950")
kw_n <- kw_df %>% 
  unnest_tokens(word, text) %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE)
kable(kw_n %>% filter(n > 7))

# create a visualization of the most common words 
kw_n %>%
  filter(n > 7) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()
```

From the table and plot, we can see that there are some words like "north", "south", "china", "american", "japan", "communist", "troops", "military", "cold", "policy", "government", which are related to the causes of the Korean War.

## 3.4 the Vietnam War

```{r}
url_1 <- "https://www.britannica.com/event/Vietnam-War"
url_2 <- c("", "/French-rule-ended-Vietnam-divided", "/The-Diem-regime-and-the-Viet-Cong",
           "/The-U-S-role-grows", "/The-conflict-deepens", 
           "/The-Gulf-of-Tonkin", "/The-United-States-enters-the-war",
           "/Firepower-comes-to-naught", "/Tet-brings-the-war-home",
           "/De-escalation-negotiation-and-Vietnamization", "/The-United-States-negotiates-a-withdrawal",
           "/The-fall-of-South-Vietnam")
url <- paste0(url_1, url_2)
url_vw <- c("https://www.historylearningsite.co.uk/vietnam-war/the-causes-of-the-vietnam-war/",
            "http://www.english.illinois.edu/maps/vietnam/causes.htm",
            "https://www.historycrunch.com/causes-of-the-vietnam-war.html#/",
            "https://www.thoughtco.com/vietnam-war-origins-2361335", url,
            "http://oxfordre.com/americanhistory/view/10.1093/acrefore/9780199329175.001.0001/acrefore-9780199329175-e-353")
        

vw1 <- url_vw[1] %>%
  read_html() %>%
  html_nodes(css = 'p:nth-child(26) span , p:nth-child(16) span , 
             p:nth-child(15) , h3+ p , span+ p span')%>%
  html_text()

vw2 <- url_vw[2] %>%
  read_html() %>%
  html_nodes(css = 'blockquote~ p+ p')%>%
  html_text()

vw3 <- url_vw[3] %>%
  read_html() %>%
  html_nodes(css = '#wsite-content .paragraph font')%>%
  html_text()

vw4 <- url_vw[4] %>%
  read_html() %>%
  html_nodes(css = '#mntl-sc-page_1-0 :nth-child(1)')%>%
  html_text()
vw4 <- vw4[1:18]

vw <- c(kw1, kw2, kw3, kw4)
vw_df <- data_frame(text = vw)

for (i in 5:length(url_vw)) {
  vw_df <- rbind(vw_df, data_frame(text = url_vw[i] %>%
  read_html() %>%
  html_nodes(css = 'p')%>%
  html_text()))
}

vw_df <- rbind(vw_df, data_frame(text = url_vw[17] %>%
  read_html() %>%
  html_nodes(css = '.abstract p')%>%
  html_text()))


vw_n <- vw_df %>% 
  unnest_tokens(word, text) %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE)
kable(vw_n %>% filter(n > 25))

# create a visualization of the most common words 
vw_n %>%
  filter(n > 25) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()
```

From the table and plot, we can see that there are some words like "north", "south", "china", "u.s", "korea", "communist", "troops", "military", "army", "president" and "government", which are related to the causes of the Vietnam War.

## 3.5 the six-day war

```{r}
url_sdw <- c("https://en.wikipedia.org/wiki/Origins_of_the_Six-Day_War",
             "http://www.sixdaywar.org/content/causes.asp",
             "https://www.history.com/topics/middle-east/six-day-war", 
             "https://www.jewishvirtuallibrary.org/background-and-overview-six-day-war",
             "https://www.myjewishlearning.com/article/the-six-day-war/",
             "https://www.thehindu.com/news/international/israels-six-day-war-explained/article18960298.ece",
             "https://adst.org/2014/05/the-six-day-miracle-the-1967-arab-israeli-war-and-how-it-changed-israel/", "https://www.foreignpolicyjournal.com/2017/06/05/who-started-the-six-day-war-of-june-1967/")

sdw1 <- url_sdw[1] %>%
  read_html() %>%
  html_nodes(css = '#mw-content-text p')%>%
  html_text()

sdw2 <- url_sdw[2] %>%
  read_html() %>%
  html_nodes(css = 'div , p+ p , table+ p')%>%
  html_text()
sdw2 <- sdw2[-c(which(sdw2==""))]
sdw2 <- sdw2[-c(6, 8, 10, 12)]

sdw3 <- url_sdw[3] %>%
  read_html() %>%
  html_nodes(css = '#section_6+ p , #section_5+ p , #section_4+ p , #section_3+ p , #section_2+ p , p+ p , .not-size-d+ p , #section_1+ p , .l-wrap-left+ p')%>%
  html_text()

sdw4 <- url_sdw[4] %>%
  read_html() %>%
  html_nodes(css = 'blockquote+ p , table+ p , blockquote+ p q , blockquote > p , h3+ p , blockquote div , p+ p')%>%
  html_text()
sdw4 <- sdw4[-91]

sdw5 <- url_sdw[5] %>%
  read_html() %>%
  html_nodes(css = '.alignnone+ p , p:nth-child(11) , h2+ p , .m-content__body p:nth-child(3)')%>%
  html_text()

sdw6 <- url_sdw[6] %>%
  read_html() %>%
  html_nodes(css = 'p:nth-child(18) , p:nth-child(17) , p:nth-child(15) , p:nth-child(14) , p:nth-child(12) , p:nth-child(11) , p:nth-child(10) , p:nth-child(9) , p:nth-child(7) , p:nth-child(6) , p:nth-child(4) , p:nth-child(3)')%>%
  html_text()

sdw7 <- url_sdw[7] %>%
  read_html() %>%
  html_nodes(css = 'h5~ p , p:nth-child(6) , p:nth-child(5)')%>%
  html_text()
sdw7 <- sdw7[-c(46, 47)]

sdw8 <- url_sdw[8] %>%
  read_html() %>%
  html_nodes(css = 'h2~ p+ p , p~ h2+ p')%>%
  html_text()

sdw <- c(sdw1, sdw2, sdw3, sdw4, sdw5, sdw6, sdw7, sdw8)
sdw_df <- data_frame(text = sdw)


sdw_n <- sdw_df %>% 
  unnest_tokens(word, text) %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE)
kable(sdw_n %>% filter(n > 30))

# create a visualization of the most common words 
sdw_n %>%
  filter(n > 30) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()
```

From the table and plot, we can see that there are some words like "israel", "arab", "egypt", "syria", "jordan", "military", "nasser", "government", "bank" and "president", which are related to the causes of the six-day war.

## 3.6 the Afghanistan War

```{r}
url_aw <- c("https://www.britannica.com/event/Afghanistan-War", 
            "https://www.cfr.org/timeline/us-war-afghanistan", 
            "https://en.wikipedia.org/wiki/War_in_Afghanistan_(2001%E2%80%93present)", 
            "https://en.wikipedia.org/wiki/War_in_Afghanistan_(1978%E2%80%93present)", 
            "https://www.mei.edu/publications/causes-and-consequences-destabilization-afghanistan",
            "https://www.brookings.edu/opinions/pakistans-role-in-the-afghanistan-wars-outcome/")

aw1 <- url_aw[1] %>%
  read_html() %>%
  html_nodes(css = 'p')%>%
  html_text()
aw1 <- aw1[-c(33:38)]

aw2 <- url_aw[2] %>%
  read_html() %>%
  html_nodes(css = '.content-text p')%>%
  html_text()

aw3 <- url_aw[3] %>%
  read_html() %>%
  html_nodes(css = '.mw-parser-output > p')%>%
  html_text()

aw4 <- url_aw[4] %>%
  read_html() %>%
  html_nodes(css = 'p')%>%
  html_text()

aw5 <- url_aw[5] %>%
  read_html() %>%
  html_nodes(css = '#main-container p+ p')%>%
  html_text()
aw5 <- aw5[-11]

aw6 <- url_aw[6] %>%
  read_html() %>%
  html_nodes(css = '.post-body-enhanced p')%>%
  html_text()
aw6 <- aw6[-c(which(aw6==""))]
aw6 <- aw6[-c(7, 11)]

aw <- c(aw1, aw2, aw3, aw4, aw5, aw6)
aw_df <- data_frame(text = aw)


aw_n <- aw_df %>% 
  unnest_tokens(word, text) %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE)
kable(aw_n %>% filter(n > 60))

# create a visualization of the most common words 
aw_n %>%
  filter(n > 60) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()
```


## 3.7 the Iraq War

```{r}
url_iw <- c("https://en.wikipedia.org/wiki/Iraq_War", 
            "https://www.britannica.com/event/Iraq-War", 
            "http://duckofminerva.com/2013/07/what-caused-the-iraq-war-a-debate-part-1-of-2.html", 
            "https://www.e-ir.info/2015/03/09/one-war-many-reasons-the-us-invasion-of-iraq/", 
            "https://archive.nytimes.com/www.nytimes.com/ref/timestopics/topics_iraq.html?scp=8&sq=the%2525",
            "https://www.cnn.com/2013/03/19/opinion/iraq-war-oil-juhasz/index.html")

iw1 <- url_iw[1] %>%
  read_html() %>%
  html_nodes(css = '.tright+ ul li , #mw-content-text h3+ ul li , .mw-parser-output > p , .tright~ p+ ul li , p+ p')%>%
  html_text()

iw2 <- url_iw[2] %>%
  read_html() %>%
  html_nodes(css = 'section > p')%>%
  html_text()

iw3 <- url_iw[3] %>%
  read_html() %>%
  html_nodes(css = '.post-content p+ p')%>%
  html_text()

iw4 <- url_iw[4] %>%
  read_html() %>%
  html_nodes(css = '.category-terrorism p')%>%
  html_text()
iw4 <- iw4[-c(54:102)]

iw5 <- url_iw[5] %>%
  read_html() %>%
  html_nodes(css = 'p')%>%
  html_text()

iw6 <- url_iw[6] %>%
  read_html() %>%
  html_nodes(css = '.zn-body__paragraph')%>%
  html_text()

iw <- c(iw1, iw2, iw3, iw4, iw5, iw6)
iw_df <- data_frame(text = iw)


iw_n <- iw_df %>% 
  unnest_tokens(word, text) %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE)
kable(iw_n %>% filter(n > 45))

# create a visualization of the most common words 
iw_n %>%
  filter(n > 45) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()
```

# 4 The Common Causes for the Listed 7 Wars

```{r}
library(plyr)
cc <- join_all(list(ww1_n, ww2_n, kw_n, vw_n, sdw_n, aw_n, iw_n), by='word', type='inner')
#cc <- inner_join(ww1_n, ww2_n, by = "word") 
```




